A Minimal Demo of \texttt{glyphmaps}

### 2012-06-07 paper/paper.Rnw
Changed options on paper. Trying to get cache to work.

<<setup,echo=FALSE,results=hide,message=FALSE>>=
# this is equivalent to \SweaveOpts{...}
opts_chunk$set(fig.path='figure/minimal-', fig.align='center', fig.show='hold', fig.lp='fig:')
opts_knit$set(cache = TRUE)
opts_knit$set(tidy = FALSE)
opts_knit$set(replace.assign=TRUE, width=90)
setwd("/Users/GarrettsiMac/Documents/git/ggplyr")
library(devtools)
load_all("../ggplyr")
@

@@

\subsection{ply$\_$aes}

\texttt{ply$\_$aes} wraps a layer like \texttt{grid} or \texttt{glyph} and causes the aesthetics to be calculated in a groupwise manner. Users can specify the groups to use, or \texttt{ply$\_$aes} will default to any groupings provided by glyph.by or group.by parameters, or a group aesthetic.

>>>>

<<setup,echo=FALSE,results=hide,message=FALSE>>=
# this is equivalent to \SweaveOpts{...}
opts_chunk$set(fig.path='figure/', fig.align='center', fig.show='hold', fig.lp='fig:', cache.path = 'cache/', cache = TRUE, tidy = FALSE)
opts_knit$set(replace.assign=TRUE, width=90)
setwd("/Users/GarrettsiMac/Documents/git/ggplyr")
library(devtools)
load_all("../ggplyr")
@

@@

\subsection{ply\_aes}

\texttt{ply\_aes} wraps a layer like \texttt{grid} or \texttt{glyph} and causes the aesthetics to be calculated in a groupwise manner. Users can specify the groups to use, or \texttt{ply$\_$aes} will default to any groupings provided by glyph.by or group.by parameters, or a group aesthetic.
